Leadership across cultures and contexts: an exploratory analysis

### 2020-06-18 leadership_across_cultures_contexts.Rmd
Removed a few "see"

In contrast to the qualities and functions dimensions, operationalizations of the costs and benefits of leadership were developed *a priori* based on theoretical literature. For both followers and leaders, we coded evidence of costs paid or benefits received in the following categories: social status, reduced or increased risk of harm or conflict, social services, territory, mating, fitness, food resources, material resources, and other miscellaneous costs or benefits not captured by these categories. See Table S\@ref(tab:costbenefitvars). Some of the costs and benefits (e.g., mating) were similar to leader qualities (e.g., polygyny). The distinction is that costs and benefits were transactional whereas qualities were descriptive (e.g., leaders obtain wives vs. have wives).

@@

ZG and KS then discussed every instance of disagreement between their respective coding on all leadership dimensions and group structure variables to produce a consensus matrix, which is used in the analyses here and added to the published data repository (in a data frame named *leader_text2*). For an illustration of the coding process, see the *Coding example* section of the supplementary information (SI).

@@

The majority of text records pertained to male leadership (`r male_leader_pct`%) and very few pertained to female leadership (`r female_leader_pct`%), with the remaining records not sex-specific. See Table S\@ref(tab:fourfactorsumm). There were female leaders in almost all contexts, however, except military and religious. Female leaders did tend to lead within kin and residential subgroups, though: `r female_residential_pct`% of female leaders led at the residential subgroup level, for instance, compared to `r male_residential_pct`% of male leaders. The majority of text records which exclusively described female leaders were from horticulturalists (`r female_hort_pct`%). See Table S\@ref(tab:sexsubtable).

@@

For each of the `r length(c(quality_vars, function_vars, leader_cost_vars, leader_benefit_vars, follower_benefit_vars, follower_cost_vars))` coded dimensions (see Tables S\@ref(tab:qualfuncvars) and S\@ref(tab:costbenefitvars)), we computed the proportion of text records (95% CI) that provided support and then computed the proportion of cultures with at least one text record providing support for that dimension (as described in the Methods section). See Figure \@ref(fig:varsupport). For a table of all coefficients and 95% CIs, see Table S\@ref(tab:glmmcoefs).

@@

The random intercepts indicated that support for many variables did vary modestly by ethnographer and culture. Most of the standard deviations of the random author and culture intercepts for each model were between 0 and 1 (on the scale of the linear predictor). See Figures S\@ref(fig:FunctionRE) and S\@ref(fig:QualityRE). In a few cases, one or the other was exactly 0, which can occur in models like ours that have many random effect levels (e.g., `r length(unique(all_data$author_ID))` authors) and a relatively small data set [@bates2015].

>>>>

In contrast to the qualities and functions dimensions, operationalizations of the costs and benefits of leadership were developed *a priori* based on theoretical literature. For both followers and leaders, we coded evidence of costs paid or benefits received in the following categories: social status, reduced or increased risk of harm or conflict, social services, territory, mating, fitness, food resources, material resources, and other miscellaneous costs or benefits not captured by these categories (Table S\@ref(tab:costbenefitvars)). Some of the costs and benefits (e.g., mating) were similar to leader qualities (e.g., polygyny). The distinction is that costs and benefits were transactional whereas qualities were descriptive (e.g., leaders obtain wives vs. have wives).

@@

ZG and KS then discussed every instance of disagreement between their respective coding on all leadership dimensions and group structure variables to produce a consensus matrix, which is used in the analyses here and added to the published data repository (in a data frame named *leader_text2*). See the *Coding example* section of the supplementary information (SI).

@@

The majority of text records pertained to male leadership (`r male_leader_pct`%) and very few pertained to female leadership (`r female_leader_pct`%), with the remaining records not sex-specific (Table S\@ref(tab:fourfactorsumm)). There were female leaders in almost all contexts, however, except military and religious. Female leaders did tend to lead within kin and residential subgroups, though: `r female_residential_pct`% of female leaders led at the residential subgroup level, for instance, compared to `r male_residential_pct`% of male leaders. The majority of text records which exclusively described female leaders were from horticulturalists (`r female_hort_pct`%) (Table S\@ref(tab:sexsubtable)).

@@

For each of the `r length(c(quality_vars, function_vars, leader_cost_vars, leader_benefit_vars, follower_benefit_vars, follower_cost_vars))` coded dimensions (Tables S\@ref(tab:qualfuncvars) and S\@ref(tab:costbenefitvars)), we computed the proportion of text records (95% CI) that provided support and then computed the proportion of cultures with at least one text record providing support for that dimension (as described in the Methods section). See Figure \@ref(fig:varsupport). For a table of all coefficients and 95% CIs, see Table S\@ref(tab:glmmcoefs).

@@

The random intercepts indicated that support for many variables did vary modestly by ethnographer and culture. Most of the standard deviations of the random author and culture intercepts for each model were between 0 and 1, on the scale of the linear predictor (Figures S\@ref(fig:FunctionRE) and S\@ref(fig:QualityRE)). In a few cases, one or the other was exactly 0, which can occur in models like ours that have many random effect levels (e.g., `r length(unique(all_data$author_ID))` authors) and a relatively small data set [@bates2015].
